Reduced growth due to belowground sink limitation is not fully explained by reduced photosynthesis

### 2017-06-27 manuscript/manuscript_pve.Rmd
updated tables for manuscript

```{r table3, echo=FALSE, warning=FALSE}
dust(table3)%>%
  sprinkle_colnames("Volume (L)", 
                        "*A*~max~ ($\\mu$mol m^-2^ s^-1^)", 
                        "*R*~dark~ ($\\mu$mol m^-2^ s^-1^)",
                        "*J*~max~ ($\\mu$mol m^-2^ s^-1^)",
                        "*V*~cmax~ ($\\mu$mol m^-2^ s^-1^)",
                        "*g*~s~ (mol m^-2^ s^-1^)",
                        "*g*~1~") %>%
  sprinkle(rows= 1, part="head",bold=TRUE)%>%
  sprinkle_print_method("markdown")
```

>>>>

```{r table3, echo=FALSE, warning=FALSE}
dust(table3)%>%
  sprinkle_colnames("Volume (L)", 
                        "*A*~max~ ($\\mu$mol m^-2^ s^-1^)", 
                        "*A*~sat~ ($\\mu$mol m^-2^ s^-1^)",
                        "*R*~dark~ ($\\mu$mol m^-2^ s^-1^)",
                        "*J*~max~ ($\\mu$mol m^-2^ s^-1^)",
                        "*V*~cmax~ ($\\mu$mol m^-2^ s^-1^)",
                        "*g*~s~ (mol m^-2^ s^-1^)",
                        "*g*~1~") %>%
  sprinkle(rows= 1, part="head",bold=TRUE)%>%
  sprinkle_print_method("markdown")
```
